Towards Transparency and Open Science

### 2023-08-08 manuscript.Rmd
use ghostscript to generate PDF/A

\includepdf[pages=-, offset=7mm 0mm,frame=false]{papers/workflow.pdf}

@@

\includepdf[pages=-, offset=7mm 0mm]{papers/tutorial.pdf}

@@

\includepdf[pages=-, offset=7mm 0mm]{papers/prereg.pdf}

>>>>

\includepdf[pages=-, width=\paperwidth - 12mm, offset=12mm 0]{papers/workflow.pdf}

@@

\includepdf[pages=-, width=\paperwidth - 12mm, offset=12mm 0]{papers/tutorial.pdf}

@@

\includepdf[pages=-, width=\paperwidth - 12mm, offset=12mm 0]{papers/prereg.pdf}
